### 2012-11-30 protein.tex
second commit

It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The cell has a built in method of ensuring that minicelling during cell division deos not occur.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.  During an oscillation period, MinD accumulates at the end of the cell in a polar zone.  It is membrane-associated in its ATP bound form, and while membrane associated it recruits MinC to the cell wall (blocking FtsZ formation).  Meanwhile the MinE forms a cytoplasmic ring at the edge of the MinD polar zone with some MinE in the zone itself.  The MinD zone shrinks and builds up on the other side of the cell.  Huang's simulation involves basic interactions between the MinD, MinE, and ATP.  MinD:ATP builds up on the membrane, where it interacts with cytoplasmic MinE that activates hydrolisis and MinE and MinD:ADP enter back into the cell.

>>>>

Bump.fdsfdsfds
It is vital during the process of bacterial cell division for proper nucleiod occlusion that the FtsZ polymer chain develop on the cell wall in the center of the cell.  Huang et all have shown in simulation that a system of Min protein interaction within the cell will lead to a natural oscillation of the MinC protein from one cell end to the other that will leave the center free of any build up of MinC.  This will allow for the PtsZ chain to develop in the center and not at the ends, where the two nucleiods are housed.  The cell has a built in method of ensuring that minicelling during cell division deos not occur.  The interaction takes place between MinE,MinD, and MinC, which naturally associates with MinD.  During an oscillation period, MinD accumulates at the end of the cell in a polar zone.  It is membrane-associated in its ATP bound form, and while membrane associated it recruits MinC to the cell wall (blocking FtsZ formation).  Meanwhile the MinE forms a cytoplasmic ring at the edge of the MinD polar zone with some MinE in the zone itself.  The MinD zone shrinks and builds up on the other side of the cell.  Huang's simulation involves basic interactions between the MinD, MinE, and ATP.  MinD:ATP builds up on the membrane, where it interacts with cytoplasmic MinE that activates hydrolisis and MinE and MinD:ADP enter back into the cell.
